Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-06 Manuscript.Rmd
Stored the permutation results, now with pvalues relative to null dist in manuscript

``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
# Based on Yeo et al. 17 network parcellation
# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
Yeo_labels <- c("L_25_",
                "L_OFC_",
                "L_10v_",
                "L_s32_",
                "L_TE1a_",
                "L_STSva_",
                "L_8ad_",
                "L_9p_",
                "L_23d_",
                "L_d23ab_",
                "L_31a_",
                "L_31pv_",
                "L_31pd_",
                "L_7m_",
                "L_v23ab_",
                "L_p24_",
                "L_d32_",
                "L_9m_",
                "L_p32_",
                "L_a24_",
                "L_10r_",
                "L_10d_",
                "L_9a_",
                "L_p10p_",
                "L_PCV_",
                "L_POS1_",
                "L_RSC_",
                "L_25_",
                "R_OFC_",
                "R_10v_",
                "R_s32_",
                "R_TE1a_",
                "R_STSva_",
                "R_8ad_",
                "R_9p_",
                "R_23d_",
                "R_d23ab_",
                "R_31a_",
                "R_31pv_",
                "R_31pd_",
                "R_7m_",
                "R_v23ab_",
                "R_p24_",
                "R_d32_",
                "R_9m_",
                "R_p32_",
                "R_a24_",
                "R_10r_",
                "R_10d_",
                "R_9a_",
                "R_p10p_",
                "R_PCV_",
                "R_POS1_",
                "R_RSC_")

@@

# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
# Minus PGi and PGs. This replicates the 7m finding. 
# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
Yeo_labels <- c("L_25_ROI",
                "L_OFC_ROI",
                "L_10v_ROI",
                "R_25_ROI",
                "R_OFC_ROI",
                "R_10v_ROI",
                "L_s32_ROI",
                "L_RSC_ROI",
                "R_RSC_ROI",
                "R_8Ad_ROI",
                "R_9p_ROI",
                "R_23d_ROI",
                "R_d23ab_ROI",
                "R_31a_ROI",
                "R_31pv_ROI",
                "R_31pd_ROI",
                "R_7m_ROI",
                "R_v23ab_ROI",
                "R_p24_ROI",
                "R_d32_ROI",
                "R_9m_ROI",
                "R_p32_ROI",
                "R_a24_ROI",
                "R_10r_ROI",
                "R_10d_ROI",
                "L_8Ad_ROI",
                "L_9p_ROI",
                "L_23d_ROI",
                "L_d23ab_RO",
                "L_31a_ROI",
                "L_31pv_ROI",
                "L_31pd_ROI",
                "L_7m_ROI",
                "L_v23ab_ROI",
                "L_p24_ROI",
                "L_d32_ROI",
                "L_9m_ROI",
                "L_p32_ROI",
                "L_a24_ROI",
                "L_10r_ROI",
                "L_10d_ROI",
                "R_s32_ROI",
                "R_9a_ROI",
                "L_p10p_ROI",
                "L_PCV_ROI")

@@

# Perform the prop test for each pair and get the max chi-squared stat
tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)})

plot(density(nullDist))

quantile(nullDist, 0.95)

tmpDF %>% filter(Chi_squared > quantile(nullDist,0.95))
```

``` {r ROI computation, echo=FALSE, message = FALSE}
# Based on Yeo et al. 17 network parcellation
# These only include areas in the medial wall belonging to DMN + OFC (changed on 12/4/18)
Yeo_labels <- c("_25_",
                "_OFC_",
                "_10v_",
                "_s32_",
                "_TE1a_",
                "_STSva_",
                "_8ad_",
                "_9p_",
                "_23d_",
                "_d23ab_",
                "_31a_",
                "_31pv_",
                "_31pd_",
                "_7m_",
                "_v23ab_",
                "_p24_",
                "_d32_",
                "_9m_",
                "_p32_",
                "_a24_",
                "_s32_",
                "_10r_",
                "_10d_",
                "_9a_",
                "_p10p_",
                "_PCV_",
                "_POS1_",
                "_RSC_")

## ROI definition
# First, load the raw count csv files
valCounts <- read.csv2('decCounts.csv', sep = ",")
dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")

@@

# Then, get the means of the counts per domain
tempBoot <- bootstrap(valCounts$Counts)
BV <- round(mean(tempBoot))
BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
tempBoot <- bootstrap(dmnCounts$Counts)
BD <- round(mean(tempBoot))
BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
rm(tempBoot)

@@

>>>>

``` {r ROI computation from Matlab, echo=FALSE, message = FALSE}
# This version is literally what I had selected originally, plus 25, OFC, 10v, and RSC; 
# Minus PGi and PGs. This replicates the 7m finding. 
# But if I add L_s32 in accord with our meeting on 12/4/18, then that's significant too
Yeo_labels <- c("L_25_ROI",
                "L_OFC_ROI",
                "L_10v_ROI",
                "R_25_ROI",
                "R_OFC_ROI",
                "R_10v_ROI",
                "L_s32_ROI",
                "L_RSC_ROI",
                "R_RSC_ROI",
                "R_8Ad_ROI",
                "R_9p_ROI",
                "R_23d_ROI",
                "R_d23ab_ROI",
                "R_31a_ROI",
                "R_31pv_ROI",
                "R_31pd_ROI",
                "R_7m_ROI",
                "R_v23ab_ROI",
                "R_p24_ROI",
                "R_d32_ROI",
                "R_9m_ROI",
                "R_p32_ROI",
                "R_a24_ROI",
                "R_10r_ROI",
                "R_10d_ROI",
                "L_8Ad_ROI",
                "L_9p_ROI",
                "L_23d_ROI",
                "L_d23ab_RO",
                "L_31a_ROI",
                "L_31pv_ROI",
                "L_31pd_ROI",
                "L_7m_ROI",
                "L_v23ab_ROI",
                "L_p24_ROI",
                "L_d32_ROI",
                "L_9m_ROI",
                "L_p32_ROI",
                "L_a24_ROI",
                "L_10r_ROI",
                "L_10d_ROI",
                "R_s32_ROI",
                "R_9a_ROI",
                "L_p10p_ROI",
                "L_PCV_ROI")

@@

@@

# Perform the prop test for each pair and get the max chi-squared stat + pvalue based on the computed null distribution
tmpDF$Chi_squared <- apply(tmpDF[,2:3], 1, function(data) {
  round(prop.test(data, c(length(studyList_sv), length(studyList_dmn)))$statistic, digits = 2)
  })
tmpDF$Pval <- 1 - ecdf(nullDist)(tmpDF$Chi_squared) # probability of finding a chi-squared stat at least as large as the observed under a permuted null distribution

# ROIs that survived the threshold based on Chi-squared value (>95th quantile from null distribution -> 8.43)
significantROIs <- tmpDF %>% filter(Chi_squared >= quantile(nullDist,0.95))

``` {r ROI computation, echo=FALSE, message = FALSE}
#TO DO: CHANGE THIS SO IT'S BASED ON STUDYLIST_SV/DMN, COUNTING JUST LIKE IN THE PERMUTATION ABOVE
## ROI definition
# First, load the raw count csv files
valCounts <- read.csv2('decCounts.csv', sep = ",")
dmnCounts <- read.csv2('dmnCounts.csv', sep = ",")

# Then, get the means of the counts per domain, both within/outside the search space
# This is to get a broad estimate of the average report amounts in the literature
tempBoot <- bootstrap(valCounts$Counts)
BV <- round(mean(tempBoot))
BVquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
tempBoot <- bootstrap(dmnCounts$Counts)
BD <- round(mean(tempBoot))
BDquant <- round(quantile(tempBoot, c(0.025, 0.975)), digits = 2)
rm(tempBoot)

@@

@@

# final overlap
bothLbls <- dmnLbls[dmnLbls %in% valLbls]
